Pyro&thinsp;-Velocity

### 2024-07-28 nbs/index.qmd
nit(nbs): fix dash spacing
Signed-off-by: Cameron Smith <cameron.ray.smith@gmail.com>

---
title: Pyro-Velocity
description: "𝒫robabilistic modeling of RNA velocity ⬱"
format:
  html:
    toc: false

about:
  id: information
  template: jolla
  image: _static/logo.png
  links: 
    - icon: download
      href: guides/installation.qmd
    - icon: book
      href: tutorials/introduction.qmd
    - icon: github
      text: GitHub
      href: https://github.com/pinellolab/pyrovelocity
---

>>>>

---
title: Pyro&thinsp;-Velocity
description: "𝒫robabilistic modeling of RNA velocity ⬱"
format:
  html:
    toc: false
about:
  id: information
  template: jolla
  image: _static/logo.png
  links: 
    - icon: download
      href: guides/installation.qmd
    - icon: book
      href: tutorials/introduction.qmd
    - icon: lightbulb
      text: Usage
      href: templates/user_example/user_example.qmd
    - icon: box-arrow-in-right
      text: Contributing
      href: about/contributing.qmd
    - icon: code-slash
      text: Source
      href: https://github.com/pinellolab/pyrovelocity
---
